\problemname{Home Renovation}
Bob has recently been renovating his house, and he has finally gotten around to renovating his bathroom.
Bob started off by removing his old sink and installing a new one.
Now Bob has removed his toilet.

Bob found the documentation on how the pipes were installed and realized it resembled a series of tubes.
Water drains from the sink and toilet into one pipe each
These two drain pipes connect to a larger pipe system made up of pipes and manifolds, which eventually drain into the sewer.

Bob now wants to install a new pipe with the smallest capacity, while not decreasing total water flow to the sewer.
Therefore, Bob has asked you to figure out how small a waste pipe can be installed without decreasing water flow.

\begin{Input}
The first line of input contains 6 integers:

\begin{itemize}
 \item $3 \le p \le 1000$: the number of pipes
 \item $\left\lceil \frac{1+\sqrt{1+4p}}{2} \right\rceil \le m \le p+1$: the number of manifolds
 \item $s_t$: the drain for the toilet, which Bob wants to minimize in size
 \item $s_s$: the drain for the sink ($s_s \ne s_t$)
 \item $m_t$: the manifold which the toilet pipe connects to ($m_t \ne s_s$, $m_t \ne s_t$)
 \item $t$: the manifold which connects to the sewer ($t \ne s_s$, $t \ne s_t$, $t \ne m_t$)
\end{itemize}
What follows is $p$ lines containing 3 integers $v$, $u$, $v \ne u$, and $1 \le c \le 10^4$, indicating a pipe from manifold $v$ to manifold $u$ with a capacity of $c$.
\end{Input}

It is guaranteed, that there always exists a pipe from $s_t$ to $m_t$, and that this is the only pipe originating from $s_t$.
Likewise, it is also guaranteed that both the toilet and sink drains contribute to the flow.

\begin{Output}
The output should contain exactly one integer, the minimum size of the waste pipe from the toilet, which does not impact the maximum water flow.
\end{Output}

